\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{LUMP: Locking and Unlocking Mobile Platform}

### 2013-05-05 paper.tex
add ssl content and libraries to server side section

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{L.U.M.P.: Locking and Unlocking Mobile Platform}} % Article title

@@

While a great deal of research has gone into software-based security on mobile devices, the technologies of hardware and software have not been combined to work together. Furthermore, even with the explosion of mobile computing in the last decade, there have been few mainstream implementations of systems that leverage mobile devices to control physical locks. With an iOS application, an Arduino Uno, a servo motor, and a Raspberry Pi, we leverage technologies such as SSL and Firmata to allow for secure connections from a mobile app to induce mechanical latches which act as locks.

@@

The server side architecture is made up of a couple of different layers. The top layer is a Python server that only accepts HTTPS requests, in order to ensure security. The server simply listens for locking and unlocking requests. Upon receiving a request, it checks the parameters of the request to ensure that the proper identifier for that particular lock has been passed. The server also sends serial information to the hardware when processing the requests, which will be discussed in more detail below. \\

@@

>>>>

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{LUMP: Locking and Unlocking Mobile Platform}} % Article title

@@

While a great deal of research has gone into software-based security on mobile devices, the technologies of hardware and software have not been combined to work together. Furthermore, even with the explosion of mobile computing in the last decade, there have been few mainstream implementations of systems that leverage mobile devices to control physical locks. With an iOS application, an Arduino Uno, a servo motor, and a Raspberry Pi, we leverage technologies such as SSL and Firmata to allow for secure connections from a mobile app to engage mechanical latches which act as locks.

@@

The server side architecture is made up of a couple of different layers. The top layer is a Python server that only accepts HTTPS requests, in order to ensure security. The server simply listens for locking, unlocking, and creation requests. Upon receiving a request, it checks the parameters of the request to ensure that the proper identifier for that particular lock has been passed. The server also sends serial information to the hardware when processing the requests, which will be discussed in more detail below. \\

The server uses two python libraries in conjunction, \texttt{ssl} \cite{pyssl} and \texttt{BaseHTTPServer} \cite{BaseHTTPServer}, which enable a basic http server to run with an ssl socket enabled. With this, we are able to keep this server running and accepting connections, but only responding to secure requests such that the metadata sent with each request cannot be seen by third parties. \\

@@

\bibitem{BaseHTTPServer}
"20.18. BaseHTTPServer --- Basic HTTP server --- Python v2.7.4 documentation." Overview --- Python v2.7.4 documentation. http://docs.python.org/2/library/basehttpserver.html (accessed May 5, 2013).

\bibitem{pyssl}
tes. "17.3. ssl --- TLS/SSL wrapper for socket objects --- Python v2.7.4 documentation." Overview --- Python v2.7.4 documentation. http://docs.python.org/2/library/ssl.html (accessed May 5, 2013).
